Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-22 Arxiv/main.tex
update efficiency plots

Our choice to use Hellinger distance is motivated by three facts:
\begin{itemize}
\item It simplifies calculations in the case of the probabilistic models considered here.
\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
\item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy a lot by applying a smooth upper bound on local sensitivity.
\begin{figure}[ht]
\centering
\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
\caption{\footnotesize{Sensitivity of $\hellinger$}}
\label{fig_sensitivity}
\end{figure}
\end{itemize}

@@

This equation is validated by experimental result shown in Fig. \ref{fig_efficiency}. We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$. It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size50to100.eps}}
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure}

>>>>

Our choice to use Hellinger distance is motivated by three facts:
\begin{itemize}
\item It simplifies calculations in the case of the probabilistic models considered here.
\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
\item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy a lot by applying a smooth upper bound on local sensitivity.
\begin{figure}[ht]
\centering
\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
\caption{{Sensitivity of $\hellinger$}}
\label{fig_sensitivity}
\end{figure}
\end{itemize}

@@

This equation is validated by an experimental result shown in Fig. \ref{fig_efficiency}. We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$. It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[data size range from 50 to 100]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size50to100.eps}}
  \subfigure[data size range from 100 to 200]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size100to200.eps}} 
  \subfigure[data size range from 200 to 500]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
  \subfigure[data size range from 500 to 1000]{
    \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure}
